``FISTA'' in Banach spaces with adaptive discretisations

### 2021-10-06 response.tex

We would like to thank both the reviewers for their time and feedback. All changes are marked in the supplementary pdf and a detailed response to each reviewer is given below.

\section{Detailed response to first reviewer}

\begin{enumerate}
	\item \review{The authors base much of the analysis on the objective function and its convergence properties \ldots it would be interesting to know how the solutions $u_n$ converge for the various versions of FISTA.}

	We thank the reviewer for their suggestion but it seems quite challenging to make a general statement. As in your comment, if one has coercivity then the sequence convergences strongly. Similarly, if one has (weakly) compact sub-levelsets, such as in the LASSO examples, then a sub-sequence converges (weakly).

	Of course there are variants of FISTA that guarantee weak convergence in the Hilbert space setting without any further coercivity or compactness assumptions. It is likely that the same arguments (e.g. [10]) can be made for our adaptive algorithm in a Hilbert space, although we haven't verified this special case. It is beyond the scope of this work to extend these results into the generalised setting and at the moment the question does not appear to be trivial.

@@

	\item \review{On page 18, the authors state: ``Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms.''}

	\review{This is used to argue that the adaptive schemes are better as they require smaller problems, less memory and less time to get to this point. However, it would appear that Figure 2 indicates that if a sufficiently accurate solution were desired, instead of a point with $E_0(u_n)\leq 0.1$, then we would still need orders of magnitude of 10 more iterations to get to the same accuracy as the nonadaptive schemes.}

	We have updated Figure 2 to show both discrete and continuous gaps to improve clarity. The point of Figure 2 (and 3) is to demonstrate the accuracy of our theoretical rate predictions. While the initial rate of convergence is faster for the nonadaptive schemes, Figure 4 confirms that this does not translate to a large practical improvement.
\end{enumerate}

\section{Detailed response to second reviewer}
We are very sorry that you found our manuscript so difficult to read. You were right, the former foundations were not rigorous enough. We have rewritten these sections in line with your suggestion of removing the emphasis on the Banach space. The analysis of the algorithm in the first half of the manuscript is now performed without mention of a Banach space. Consequently, we also realised that the subspace structure and orthogonal projection were not required either. We now allow $U^n$ to be closed convex subsets of $\F H$. The Banach space setting is reserved for examples discussed in Section 5 onwards.

### 2021-10-13 response.tex

	\item \review{page 12 and elsewhere: $\partial E$ is usually referred to as the subdifferential. I suppose this depends on the literature source you use.}

	As suggested, we have switched to using the term `subdifferential' throughout the document.

	\item \review{My only ``disappointment'' with the paper is that the theory is illustrated with LASSO. As a result, $E$ has a rather favorable structure. There are many examples, e.g., in robust statistics, where it would be more appropriate to use the $\ell^1$ norm instead of the $\ell^2$ norm for misfit. Since the favorable properties of the squared $\ell^2$-norm are often used in the derivations (bounds, constants, etc. in Section 6), I wonder how hard it would be to do the same for other relevant examples.}

	You are right, we can also consider alternative misfits. We have replaced the wavelet example in Section 7.2 with a (Huber-smoothed) robust $\ell^1$ penalty. This also led to a number of small updates to the analysis in Section 6 to generalise for a non-quadratic misfit.

### 2021-10-13 paper.tex
Added new reference
Added Data statement section

\usepackage{amsmath,enumitem,datetime,xfrac,fix-cm,color,multirow,siunitx}
\usepackage{amssymb,mathtools,stmaryrd,dsfont,tikz}
\usepackage{fullpage}
\usepackage[colorlinks, citecolor=blue, bookmarks=True]{hyperref}
\usetikzlibrary{positioning,trees}
\usepackage{algorithm,algpseudocode}
\graphicspath{{Figures/}}
\DeclareGraphicsExtensions{.pdf,.png}

\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\tens{A}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}
\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\newcommand{\1}{\F{1}}
\DeclareMathOperator{\st}{\;s.t.\;}
\renewcommand{\epsilon}{\varepsilon}\renewcommand{\bar}{\overline}
\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\sign}{sign}
\newcommand{\Emin}[1][\varf0]{\inf_{#1\in\F H}\op{E}(#1)}

@@

% TODO: get rid of this stuff...
\usepackage{clipboard}\newclipboard{aFEMclipboard}
\usepackage{xstring}
\newcommand*{\varf}[1]{%
	\IfEqCase{#1}{%
		{0}{u}%
		{1}{v}%
		{2}{w}%
	}[u#1]%
}
\newcommand*{\Varf}[1]{%
	\IfEqCase{#1}{%
		{0}{U}%
		{1}{V}%
		{2}{W}%
	}[u#1]%
}
\newcommand*{\spcf}[1]{%
	\IfEqCase{#1}{%
		{0}{\F{U}}%
		{1}{\F{V}}%
		{2}{\F{W}}%
	}[\F{U}#1]%
}
\newcommand*{\vard}[1]{%
	\IfEqCase{#1}{%
		{0}{\varphi}%
		{1}{\psi}%
	}[\varphi #1]%
}
\newcommand*{\varx}[1]{%
	\IfEqCase{#1}{%
		{0}{x}%
		{1}{y}%
		{2}{z}%
		{3}{r}%
	}[x#1]%
}
\newcommand*{\vars}[1]{%
	\IfEqCase{#1}{%
		{0}{\alpha}%
		{1}{\beta}%
		{2}{\gamma}%
		{3}{a}%
		{4}{b}%
		{5}{c}%
	}[k#1]%
}
\newcommand*{\Vars}[1]{%
	\IfEqCase{#1}{%
		{0}{\mathrm{A}}%
		{1}{\mathrm{B}}%
		{2}{\Gamma}%
		{3}{A}%
		{4}{B}%
		{5}{C}%
	}[K#1]%
}
\newcommand{\data}{\eta}
\newcommand{\Domain}{\Omega}\newcommand{\domain}{\omega}
\newcommand{\diam}{\op{diam}}
\newcommand{\meshsize}{h}

% vector forms
\newcommand*{\vvarx}[1]{\vec{\varx{#1}}}
\newcommand*{\vvars}[1]{\vec{\vars{#1}}}
\newcommand*{\vvard}[1]{\vec{\vard{#1}}}

% Macro for tracking changes
\usepackage[normalem]{ulem}\renewcommand{\ULthickness}{1.0pt}
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
%\renewcommand{\edit}[2]{#2}
\newcommand{\todo}[1]{{\color{red}#1}}

@@

	\section{Introduction}
	The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by Beck and Teboulle \cite{Beck2009} as an extension of Nesterov's fast gradient method \cite{Nesterov2004} and is now a very popular algorithm for minimising the sum of two convex functions.
	We write this as the problem of computing
	\begin{equation}\label{eq: min F = fD+fC}
		\edit{u^* \in \argmin_{\varf0\in\F H}\op{E}(\varf0)}{\Emin}  \qquad\text{such that}\qquad \op{E}(\varf0)\coloneqq \op{f}(\varf0) + \op{g}(\varf0),
	\end{equation}
	where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute. The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$. It has been shown that $\op{E}(\varf0_n) - \edit{\op{E}(u^*)}{\Emin}$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}. Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \cite{Tao2016,Liang2017,Alamo2019}.

	The contribution of this work is a modified FISTA algorithm which achieves two key properties:
	\begin{itemize}
		\item we extend the convergence results to the case \edit{$\varf0^*\in\bar{\F H}\setminus\F H$ where $\spcf0\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved. For example, in \edit{Lasso}{L1 penalised reconstructions} discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\spcf0\supset\F H$ such that $\Emin = \min_{\varf0\in\spcf0}\op{E}(\varf0)$ is achieved in $\spcf0\setminus\F H$}. The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
		\item we allow for adaptive discretisation such that $\varf0_n\in\spcf0^n\subset\F H$. With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence. In the Hilbert space setting this is the original $n^{-2}$ rate. In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.
	\end{itemize}
	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for \edit{the use outside of Hilbert spaces}{use with un-attained minima} is the key theoretical novelty. Some other works for FISTA-like algorithms include \cite{Jiang2012,Villa2013}. Of particular note, our stability estimate for FISTA  in Theorem~\ref{thm: mini FISTA convergence} is very similar to \cite[Prop 2]{Schmidt2011} and \cite[Prop 3.3]{Aujol2015}. This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations. The ideas in \cite{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\op{g}$. The permitted refinement steps are also more broad in our work.

	\subsection{Outline}
	This work is organised as follows. Section~\ref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, Algorithm~\ref{alg: refining FISTA}. The main theoretical contribution of this work is the convergence analysis of Algorithm~\ref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in Section~\ref{sec: recipe}, then we state the specific results in the case of FISTA in Section~\ref{sec: FISTA convergence}. The main results are Theorems~\ref{thm: exponential FISTA convergence}/\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\spcf0^n$ respectively.

	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} \edit{}{in Banach spaces }and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation. In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\varf0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\varf0^*$}{the minimiser}. The numerical results in Section~\ref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.

	\section{Definitions and notation}\label{sec: prelims}
	\edit{We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\spcf0,\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
	\\\centerline{$\displaystyle \exists\varf0^*\in \spcf0 \quad\st\quad \op{E}(\varf0^*) = \min_{\varf0\in\spcf0}\op{E}(\varf0) = \inf_{\varf0\in\F H}\op{E}(\varf0).$}
	Furthermore, define the translated energy
	\\\centerline{$\displaystyle \op{E}_0\colon\spcf0\cup\F H\to \R,\qquad \op{E}_0(\varf0) \coloneqq \op{E}(\varf0)-\op{E}(\varf0^*).$}
	Note that the value of $\op{E}_0$ is uniquely defined, even if $\varf0^*$ may not be.%
	\\}{%
	We consider optimisation of \eqref{eq: min F = fD+fC} over a Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$ with the translated energy
	\begin{equation}
		\op{E}_0\colon\F H\to \R,\qquad \op{E}_0(\varf0) \coloneqq \op{E}(\varf0)-\Emin[\tilde{\varf0}].
	\end{equation}
	}

	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\spcf0^n\subset \edit{\spcf0\cap}{}\F H$ for $n\in\F N$. The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\spcf0^n$. If $\spcf0^n\edit{=\spcf0}{}=\F H$, then we recover the \edit{standard FISTA}{original} algorithm. \edit{}{More generally, the idea is that $\spcf0^n$ are `growing', for example $\spcf0^n\subset\spcf0^{n+1}$, but this assumption is not necessary in most of the results.}

	Without loss of generality we will assume $L=1$, i.e. $\nabla\op{f}$ is 1-Lipschitz. To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.\edit{ A more important distinction is to say that the properties of $\op{f}$ and $\op{g}$ are stated with respect to the Hilbert norm.}{} In particular,
	\begin{equation}
		\norm{\nabla\op{f}(\varf0)- \nabla\op{f}(\varf1)} \leq \norm{\varf0-\varf1}
	\end{equation}
	for all $\varf0,\varf1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
	\begin{equation}
		\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \op{g}(\varf0)
	\end{equation}
	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$. \edit{}{Closed subsets of $\F H$ are locally weakly compact, therefore this argmin is always non-empty.}

@@

	\edit{Finally we introduce the concept of an orthogonal projection in the setting of this work. For a subspace $\spcf0^n\subset\spcf0\cap\F H$ we define the orthogonal projection $\tens{\Pi}_n\colon (\spcf0^n)^*\to \spcf0^n$ to be any extension of the function such that 
	\\\centerline{$\IP{\tens{\Pi}_n\varf0}{\varf1} = \IP{\varf0}{\varf1} \text{ for all } \varf0\in(\spcf0^n)^*, \ \varf1\in\spcf0^n.$}
	This definition is non-standard as we view $(\spcf0^n)^*$ embedded in $\spcf0$. Note that $\spcf0^n\subset\F H$ implies that $(\spcf0^n)^*\supset\F H$, therefore $\tens{\Pi}_n$ is an extension of the classical orthogonal projection. It is convenient to allow an extension here because $\spcf0$ may be bigger than $\F H$, $(\spcf0^n)^*$ is the largest space such that $\tens{\Pi}_n$ is sufficiently well-defined. Beyond this, the Hahn-Banach theorem may allow the domain of $\tens{\Pi}_n$ to be extended further, but the definition is no longer unique. For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{\varx0}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers. To account for this possibility, we shall state that the domain of $\tens{\Pi}_n$ is $\bar{(\spcf0^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.}{}

	The precise constants associated to a given rate are given in the statements of the theorems but, for convenience, are otherwise omitted from the text. For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will use the notation:
	\begin{align*}
		a_n \lesssim b_n \qquad &\iff \qquad \exists C,N>0 \st a_n \leq C b_n \text{ for all } n>N,
		\\ a_n \simeq b_n \qquad &\iff \qquad a_n\lesssim b_n \lesssim a_n.
	\end{align*}
	\edit{}{For $n\in\F N$ we use the abbreviation $[n] = \{1,2,\ldots,n\}$. When the subdifferential of $\op{E}$ is set-valued, we will use the short-hand
	\begin{equation}
		\Norm{\partial\op{E}(\varf0)} \coloneqq \inf_{\varf1\in\partial\op{E}(\varf0)}\Norm{\varf1}
	\end{equation}
	for any specified norm $\Norm\cdot$.}

	\begin{algorithm}\caption{Refining \edit{subspace}{subset} FISTA}\label{alg: refining FISTA}
		\centering
		\begin{algorithmic}[1]
			\State Choose $(\spcf0^n)_{n\in\F N}$, $\varf0_0\in \spcf0^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
			\State $\varf1_0\gets \varf0_0, n\gets0$
			\Repeat
			\State $\bar{\varf0}_n \gets (1-\tfrac{1}{t_n})\varf0_n + \tfrac{1}{t_n}\varf1_n$
			\State $\displaystyle \varf0_{n+1} \gets \argmin_{\varf0\in \spcf0^{n+1}} \tfrac12\norm{\varf0-\bar{\varf0}_n+\nabla \op{f}(\bar{\varf0}_n)}^2+\op{g}(\varf0)$ \Comment{Only modification, $\spcf0^{n+1}\subset \spcf0$}
			\State $\varf1_{n+1} \gets (1-t_n)\varf0_n + t_n\varf0_{n+1}$
			\State $n\gets n+1$
			\Until{converged}
		\end{algorithmic}
	\end{algorithm}

	\section{General proof recipe}\label{sec: recipe}
	In this section we give an intuitive outline of the full proof for convergence of Algorithm~\ref{alg: refining FISTA} before giving formal theorems and proofs in the next section. First we recall the classical FISTA convergence guarantee given by \cite[\edit{Theorem 2}{Thm 3.1}]{Chambolle2015}:
	\begin{equation}\label{eq: classical FISTA}
		t_N^2\op{E}_0(\varf0_N) + \sum^{N-1}_{n=1}\rho_n\op{E}_0(\varf0_n) + \tfrac12\norm{\varf1_N-\varf0^*}^2 \leq \tfrac12\norm{\varf0_0-\varf0^*}^2
	\end{equation}
	for some FISTA stepsize choice $t_N\simeq N$ and $\rho_n\geq0$.

>>>>

% Define `data availability' environment like acknowledgement
\def\datavname{Data availability statement}%
\def\datav{\par\addvspace{17pt}\small\rmfamily
	\trivlist\if!\datavname!\item[]\else
	\item[\hskip\labelsep
	{\bfseries\datavname}]\fi}
\def\enddatav{\endtrivlist\addvspace{6pt}}
\newenvironment{dataavailability}{\begin{datav}}
	{\end{datav}}

\usepackage{amsmath,enumitem,datetime,xfrac,fix-cm,color,multirow,siunitx}
\usepackage{amssymb,mathtools,stmaryrd,dsfont,tikz}
\usepackage{fullpage}
\usepackage[colorlinks, citecolor=blue, bookmarks=True]{hyperref}
\usetikzlibrary{positioning,trees}
\usepackage{algorithm,algpseudocode}
%\graphicspath{{Figures/}}
\DeclareGraphicsExtensions{.pdf,.png}

\let\F\mathds\let\C\mathcal\newcommand{\R}{\F{R}}\newcommand{\A}{\tens{A}}
\newcommand{\norm}[1]{{\left\lVert #1 \right\rVert}}
\newcommand{\Norm}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
\newcommand{\IP}[2]{\left\langle #1,#2 \right\rangle}
\newcommand{\ip}[2]{#1 \vcenter{\hbox{\resizebox{6pt}{!}{\ensuremath\cdot}}} #2}
\newcommand{\op}[1]{\operatorname{#1}}
\newcommand{\splitln}[4]{\begin{cases} #1 & #2 \\ #3 & #4\end{cases}}
\newcommand{\1}{\F{1}}
\DeclareMathOperator{\st}{\;s.t.\;}
\renewcommand{\epsilon}{\varepsilon}\renewcommand{\bar}{\overline}
\renewcommand{\hat}{\widehat}\renewcommand{\tilde}{\widetilde}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\sign}{sign}
\newcommand{\Emin}[1][\var0]{\inf_{#1\in\F H}\op{E}(#1)}

@@

\usepackage{clipboard}\newclipboard{aFEMclipboard}
\newcommand{\data}{\eta}
\newcommand{\Domain}{\Omega}\newcommand{\domain}{\omega}
\newcommand{\diam}{\op{diam}}
\newcommand{\meshsize}{h}

\usepackage{xstring}
% Function variable names
\newcommand*{\var}[1]{%
	\IfEqCase{#1}{%
		{0}{u}%
		{1}{v}%
		{2}{w}%
	}[u#1]%
}
% Scalar and vector variable names
\newcommand*{\vars}[1]{%
	\IfEqCase{#1}{%
		{0}{\alpha}%
		{1}{\beta}%
		{2}{\gamma}%
		{3}{a}%
		{4}{b}%
		{5}{c}%
	}[k#1]%
}
\newcommand*{\vvars}[1]{\vec{\vars{#1}}}

% Macro for tracking changes
\usepackage[normalem]{ulem}\renewcommand{\ULthickness}{1.0pt}
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\newcommand{\edit}[2]{{\ifmmode\text{\color{red}\sout{\ensuremath{#1}}}\else {\color{red} \sout{#1}}\fi} {\color{darkgreen} #2}}
\renewcommand{\edit}[2]{#2}
%\newcommand{\todo}[1]{{\color{red}#1}}

@@

	\section{Introduction}
	The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by Beck and Teboulle \cite{Beck2009} as an extension of Nesterov's fast gradient method \cite{Nesterov2004} and is now a very popular algorithm for minimising the sum of two convex functions.
	We write this as the problem of computing
	\begin{equation}\label{eq: min F = fD+fC}
		\edit{u^* \in \argmin_{\var0\in\F H}\op{E}(\var0)}{\Emin}  \qquad\text{such that}\qquad \op{E}(\var0)\coloneqq \op{f}(\var0) + \op{g}(\var0),
	\end{equation}
	where $\op{f}\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\op{g}\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute. The iterates of the FISTA algorithm will be denoted $\var0_n\in\F H$. It has been shown that $\op{E}(\var0_n) - \edit{\op{E}(u^*)}{\Emin}$ converges at the optimum rate of $n^{-2}$ \cite{Beck2009}, and later (after a small modification) the convergence of the iterates was also shown in a general Hilbert space setting \cite{Chambolle2015}. Many further works have gone on to demonstrate faster practical convergence rates for slightly modified variants of FISTA \cite{Tao2016,Liang2017,Alamo2019}.

	The contribution of this work is a modified FISTA algorithm which achieves two key properties:
	\begin{itemize}
		\item we extend the convergence results to the case \edit{$\var0^*\in\bar{\F H}\setminus\F H$ where $\F{U}\coloneqq \bar{\F H}$ is a Banach space}{where the minimum is not achieved. For example, in \edit{Lasso}{L1 penalised reconstructions} discussed in Section~\ref{sec: Lasso definition} there exists a Banach space $\F{U}\supset\F H$ such that $\Emin = \min_{\var0\in\F{U}}\op{E}(\var0)$ is achieved in $\F{U}\setminus\F H$}. The proven rate is slower than the optimal $n^{-2}$, but appears to be quite sharp in numerical examples.
		\item we allow for adaptive discretisation such that $\var0_n\in\F{U}^n\subset\F H$. With simple guarantees on the rates of convergence, we show analytically that applying our FISTA algorithm with inexact discretisation does not reduce the proven rate of convergence. In the Hilbert space setting this is the original $n^{-2}$ rate. In numerical examples we demonstrate that greedy adaptive discretisation strategies can achieve much greater performance than uniform discretisation, both in measures of time and computer memory requirements.
	\end{itemize}
	There is much overlap between the techniques used in this work and those used in the literature of inexact optimisation, although we believe that our interpretation for \edit{the use outside of Hilbert spaces}{use with un-attained minima} is the key theoretical novelty. Some other works for FISTA-like algorithms include \cite{Jiang2012,Villa2013}. Of particular note, our stability estimate for FISTA  in Theorem~\ref{thm: mini FISTA convergence} is very similar to \cite[Prop 2]{Schmidt2011} and \cite[Prop 3.3]{Aujol2015}. This is then used to analyse the convergence properties in our more general Banach space setting where all sources of inexactness come from subspace approximations. The ideas in \cite{Parpas2017} are similar although in application to the proximal gradient method with an additional smoothing on the functional $\op{g}$. The permitted refinement steps are also more broad in our work. \cite{}{Very recent work in \cite{Yu2021} proposes a `Multilevel FISTA' algorithm which allows similar coarse-to-fine refinement strategies, although only a finite number. We also allow for non-uniform refinement with a posteriori strategies.}

	\subsection{Outline}
	This work is organised as follows. Section~\ref{sec: prelims} defines notation and the generic form of our proposed refining FISTA algorithm, Algorithm~\ref{alg: refining FISTA}. The main theoretical contribution of this work is the convergence analysis of Algorithm~\ref{alg: refining FISTA} which is split into two parts: first we outline the proof structure in Section~\ref{sec: recipe}, then we state the specific results in the case of FISTA in Section~\ref{sec: FISTA convergence}. The main results are Theorems~\ref{thm: exponential FISTA convergence}/\ref{thm: stronger exponential FISTA convergence} which extend the convergence of FISTA \edit{to infinite dimensional Banach spaces}{to cases with un-attained minima} with uniform/adaptively chosen subspaces $\F{U}^n$ respectively.

	Section~\ref{sec: general examples} presents some general results for the application of Algorithm~\ref{alg: refining FISTA} \edit{}{in Banach spaces }and Section~\ref{sec: Lasso definition} gives a much more detailed discussion of adaptive refinement for Lasso minimisation. In particular, we describe how to choose efficient refining discretisations to approximate \edit{$\var0^*$}{$\Emin$}, estimate the convergence of $\op{E}$, and identify the support of \edit{$\var0^*$}{the minimiser}. The numerical results in Section~\ref{sec: numerics} demonstrate these techniques in four different models demonstrating the apparent sharpness of our convergence rates and the computational efficiency of adaptive discretisations.

	\section{Definitions and notation}\label{sec: prelims}
	\edit{We consider optimisation of \eqref{eq: min F = fD+fC} over two spaces, the Banach space $(\F{U},\Norm\cdot)$ and Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$, such that 
	\\\centerline{$\displaystyle \exists\var0^*\in \F{U} \quad\st\quad \op{E}(\var0^*) = \min_{\var0\in\F{U}}\op{E}(\var0) = \inf_{\var0\in\F H}\op{E}(\var0).$}
	Furthermore, define the translated energy
	\\\centerline{$\displaystyle \op{E}_0\colon\F{U}\cup\F H\to \R,\qquad \op{E}_0(\var0) \coloneqq \op{E}(\var0)-\op{E}(\var0^*).$}
	Note that the value of $\op{E}_0$ is uniquely defined, even if $\var0^*$ may not be.%
	\\}{%
	We consider optimisation of \eqref{eq: min F = fD+fC} over a Hilbert space $(\F H,\IP\cdot\cdot,\norm\cdot)$ with the translated energy
	\begin{equation}
		\op{E}_0\colon\F H\to \R,\qquad \op{E}_0(\var0) \coloneqq \op{E}(\var0)-\Emin[\tilde{\var0}].
	\end{equation}
	}

	The proposed generalised FISTA algorithm is stated in Algorithm~\ref{alg: refining FISTA} for an arbitrary choice of \edit{refining subspaces}{closed convex subsets} $\F{U}^n\subset \edit{\F{U}\cap}{}\F H$ for $n\in\F N$. The only difference \edit{}{from standard FISTA }is that on iteration $n$, all computations are performed in the \edit{subspace}{subset} $\F{U}^n$. If $\F{U}^n\edit{=\F{U}}{}=\F H$, then we recover the \edit{standard FISTA}{original} algorithm. \edit{}{More generally, the idea is that $\F{U}^n$ are `growing', for example $\F{U}^n\subset\F{U}^{n+1}$, but this assumption is not necessary in most of the results.}

	Without loss of generality we will assume $L=1$, i.e. $\nabla\op{f}$ is 1-Lipschitz. To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.\edit{ A more important distinction is to say that the properties of $\op{f}$ and $\op{g}$ are stated with respect to the Hilbert norm.}{} In particular,
	\begin{equation}
		\norm{\nabla\op{f}(\var0)- \nabla\op{f}(\var1)} \leq \norm{\var0-\var1}
	\end{equation}
	for all $\var0,\var1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
	\begin{equation}
		\argmin_{\var0\in\tilde{\F{U}}}\tfrac12\norm{\var0-\var1}^2 + \op{g}(\var0)
	\end{equation}
	is exactly computable for all $\var1\in\F H$ and all $\tilde{\F{U}}\in\{\F{U}^n\}_{n=0}^\infty$. \edit{}{Closed subsets of $\F H$ are locally weakly compact, therefore this argmin is always non-empty.}

@@

	\edit{Finally we introduce the concept of an orthogonal projection in the setting of this work. For a subspace $\F{U}^n\subset\F{U}\cap\F H$ we define the orthogonal projection $\tens{\Pi}_n\colon (\F{U}^n)^*\to \F{U}^n$ to be any extension of the function such that 
	\\\centerline{$\IP{\tens{\Pi}_n\var0}{\var1} = \IP{\var0}{\var1} \text{ for all } \var0\in(\F{U}^n)^*, \ \var1\in\F{U}^n.$}
	This definition is non-standard as we view $(\F{U}^n)^*$ embedded in $\F{U}$. Note that $\F{U}^n\subset\F H$ implies that $(\F{U}^n)^*\supset\F H$, therefore $\tens{\Pi}_n$ is an extension of the classical orthogonal projection. It is convenient to allow an extension here because $\F{U}$ may be bigger than $\F H$, $(\F{U}^n)^*$ is the largest space such that $\tens{\Pi}_n$ is sufficiently well-defined. Beyond this, the Hahn-Banach theorem may allow the domain of $\tens{\Pi}_n$ to be extended further, but the definition is no longer unique. For example, in 1D the value of $\IP{\delta_0}{\frac{1}{\sqrt[4]{x}}}$ is not well-defined, but the value of $\IP{\delta_0}{\1_{[0,1]}}$ can be chosen to be consistent with some sequence of molifiers. To account for this possibility, we shall state that the domain of $\tens{\Pi}_n$ is $\bar{(\F{U}^n)^*}$, with the closure computed in an appropriate topology dictated by $\Norm\cdot$.}{}

	The precise constants associated to a given rate are given in the statements of the theorems but, for convenience, are otherwise omitted from the text. For sequences $(a_n)_{n=1}^\infty$,$(b_n)_{n=1}^\infty$ we will use the notation:
	\begin{align*}
		a_n \lesssim b_n \qquad &\iff \qquad \exists C,N>0 \st a_n \leq C b_n \text{ for all } n>N,
		\\ a_n \simeq b_n \qquad &\iff \qquad a_n\lesssim b_n \lesssim a_n.
	\end{align*}
	\edit{}{For $n\in\F N$ we use the abbreviation $[n] = \{1,2,\ldots,n\}$. When the subdifferential of $\op{E}$ is set-valued, we will use the short-hand
	\begin{equation}
		\Norm{\partial\op{E}(\var0)} \coloneqq \inf_{\var1\in\partial\op{E}(\var0)}\Norm{\var1}
	\end{equation}
	for any specified norm $\Norm\cdot$.}

	\begin{algorithm}\caption{Refining \edit{subspace}{subset} FISTA}\label{alg: refining FISTA}
		\centering
		\begin{algorithmic}[1]
			\State Choose $(\F{U}^n)_{n\in\F N}$, $\var0_0\in \F{U}^0$ and some FISTA stepsize choice $(t_n)_{n\in\F N}$
			\State $\var1_0\gets \var0_0, n\gets0$
			\Repeat
			\State $\bar{\var0}_n \gets (1-\tfrac{1}{t_n})\var0_n + \tfrac{1}{t_n}\var1_n$
			\State $\displaystyle \var0_{n+1} \gets \argmin_{\var0\in \F{U}^{n+1}} \tfrac12\norm{\var0-\bar{\var0}_n+\nabla \op{f}(\bar{\var0}_n)}^2+\op{g}(\var0)$ \Comment{Only modification, $\F{U}^{n+1}\subset \F{U}$}
			\State $\var1_{n+1} \gets (1-t_n)\var0_n + t_n\var0_{n+1}$
			\State $n\gets n+1$
			\Until{converged}
		\end{algorithmic}
	\end{algorithm}

	\section{General proof recipe}\label{sec: recipe}
	In this section we give an intuitive outline of the full proof for convergence of Algorithm~\ref{alg: refining FISTA} before giving formal theorems and proofs in the next section. First we recall the classical FISTA convergence guarantee given by \cite[\edit{Theorem 2}{Thm 3.1}]{Chambolle2015}:
	\begin{equation}\label{eq: classical FISTA}
		t_N^2\op{E}_0(\var0_N) + \sum^{N-1}_{n=1}\rho_n\op{E}_0(\var0_n) + \tfrac12\norm{\var1_N-\var0^*}^2 \leq \tfrac12\norm{\var0_0-\var0^*}^2
	\end{equation}
	for some FISTA stepsize choice $t_N\simeq N$ and $\rho_n\geq0$.
